### 2023-04-21 paper/content.tex
Updates from Overleaf

Another route to be explored in the inversion of magnetic microscopy images is
to obtain all the information, i.e. the magnetic moment and the position of the
sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
explore the techniques developed in exploration geophysics, in spite of the
differences between aeromagnetic surveys and magnetic microscopy
\citep{Lima2013}. Magnetic microscopy images commonly show the combined signal
of multiple magnetic particles and can vary greatly in wavelength, strength,
and spatial separation, depending on the natural remanent magnetization (NRM) and location of each particle. We
usually assume that the signal measured by the magnetic microscope is the
vertical component of the magnetic induction vector ($b_z$), the measurements
are performed on a regular grid with evenly spaced grid points and at a
constant height, and the data are contaminated with random Gaussian noise and
long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
we provide a methodological routine to retrieve the individual magnetic moment
of ferromagnetic grains in magnetic microscopy images following the approach
devised by \citet{Oliveira2015Estimation} for the interpretation of
aeromagnetic anomalies. The method we propose allows one to quickly and
semi-automatically estimate the individual magnetic moment vector of the stable
magnetic carriers, making use of only the magnetic images themselves and an
assumption of approximately dipolar sources. If used on a large scale, the
method provides the means to scan large areas of the rock sample, attaining
potentially the number of magnetic moments necessary for paleomagnetic studies.

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of approximatly 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data was taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Fu2020,
Glenn2017}. We applied a bias field of 0.9 mT during the measurement, which was periodically reversed to result in an effective background field of <1 µT.  After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 75 potential sources
(Figure~\ref{real-data}e).

>>>>

Another route to be explored in the inversion of magnetic microscopy images is
to obtain all the information, i.e. the magnetic moment and the position of the
sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
explore the techniques developed in exploration geophysics, in spite of the
differences between aeromagnetic surveys and magnetic microscopy
\citep{Lima2013}. Magnetic microscopy images commonly show the combined signal
of multiple magnetic particles and can vary greatly in wavelength, strength,
and spatial separation, depending on the natural remanent magnetization (NRM) and location of each particle. We
usually assume that the signal measured by the magnetic microscope is the
vertical component of the magnetic induction vector ($b_z$), the measurements
are performed on a regular grid with evenly spaced grid points and at a
constant height, and the data are contaminated with pseudorandom Gaussian noise and
long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
we provide a methodological routine to retrieve the individual magnetic moment
of ferromagnetic grains in magnetic microscopy images following the approach
devised by \citet{Oliveira2015Estimation} for the interpretation of
aeromagnetic anomalies. The method we propose allows one to quickly and
semi-automatically estimate the individual magnetic moment vector of the stable
magnetic carriers, making use of only the magnetic images themselves and an
assumption of approximately dipolar sources. If used on a large scale, the
method provides the means to scan large areas of the rock sample, attaining
potentially the number of magnetic moments necessary for paleomagnetic studies.

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of approximatly 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Lima2009, Fu2020,
Glenn2017}. We applied a bias field of \qty{0.9}{\m\tesla} during the measurement, which was periodically reversed to result in an effective background field of <1 µT.  After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 75 potential sources
(Figure~\ref{real-data}e).
